### 2022-03-23 pre/pre.tex
jasmin
wan

However, this simple approach is prohibitively expensive and modern tools that
decide propositional satisfiability problem (SAT solvers) use more advanced
approaches such as the CDCL calculus \cite{mss-96-cdcl}. Modern SAT solvers also
heavily preprocess the problem and continue simplifying it during the proving
process.

@@

Some of the approaches described in this thesis are based on {\em rank-1
polymorphism} \cite{bp-13-tff1,ksr-16-th1}. This is an extension of simply typed
logic which adds type variables to the definition of types and type arguments to
polymorphic constants (Chapter \ref{ch:bools}). It further
requires that type arguments are instantiated with concrete, non-quantified
types. In clausal structure it allows (implicit)
quantification over types only on top-level and not inside literals.

>>>>

However, this simple approach is prohibitively expensive and modern tools that
decide propositional satisfiability problem (SAT solvers) use more advanced
approaches such as the CDCL calculus \cite{mss-96-cdcl}. Crucial improvement of
this calculus compared to more naive approaches is that it does not backtrack
chronologically when it determines that the partial model constructed for a set
of clauses does not satisfy all clauses. Instead, it generates a \emph{learned
clause} which explains how this conflicting state was reached, which enables
smarter backtracking.   Modern SAT solvers also heavily preprocess the problem
and continue simplifying it during the proving process.

@@

Some of the approaches described in this thesis are based on {\em rank-1
polymorphism} \cite{bp-13-tff1,ksr-16-th1}. This is an extension of simply typed
logic which adds type variables to the definition of types and type arguments to
polymorphic constants (Chapter \ref{ch:bools}). It further
requires that type arguments are instantiated with concrete, non-quantified
types. In a clausal structure it allows (implicit)
quantification over types only on top-level and not inside literals.
